Using CopyKAT to idenfity tumor cells in Ewing sarcoma samples

### 2024-05-10 analyses/ewings-cell-type/03-copykat.Rmd
remove old notebook
Apply suggestions from code review
Co-authored-by: Joshua Shapiro <josh.shapiro@ccdatalab.org>

```{r}
caret_df <- cnv_df |> 
  dplyr::filter(copykat.pred != "not.defined") |> 
  dplyr::mutate(copykat = ifelse(
    # use str_detect for test data
    copykat.pred == "diploid", "Normal", "Tumor"
  )) |> 
  # make tumor the positive class
  dplyr::mutate(
    copykat = forcats::fct_relevel(copykat, "Tumor"),
    marker_gene_classification = forcats::fct_relevel(marker_gene_classification, "Tumor")
  ) |> 
  split(cnv_df$reference_used)

@@

Looking at these results, we see that cells classified as tumor cells using marker genes are mostly overlapping with cells that are aneuploid in CopyKAT, which is what we expect! 
We also see that the Kappa values range are close to 1, indicating almost perfect agreement.

>>>>

```{r}
filtered_cnv_df <- cnv_df |> 
  dplyr::filter(copykat.pred != "not.defined") |> 
caret_df_list <- filtered_cnv_df |> 
  dplyr::mutate(copykat = ifelse(
    # use str_detect for test data
    copykat.pred == "diploid", "Normal", "Tumor"
  )) |> 
  # make tumor the positive class
  dplyr::mutate(
    copykat = forcats::fct_relevel(copykat, "Tumor"),
    marker_gene_classification = forcats::fct_relevel(marker_gene_classification, "Tumor")
  ) |> 
  split(cnv_df$reference_used)

@@

Looking at these results, we see that cells classified as tumor cells using marker genes are mostly overlapping with cells that are aneuploid in CopyKAT, which is what we expect! 
We also see that the Kappa values are close to 1, indicating almost perfect agreement.
